An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-13 poly-embed-journal/poly-embed-journal.tex
more edits...

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
\newcommand{\reviewertwo}[1]{\reviewerresponse{blue!20!white}{R2: #1}}
\newcommand{\reviewerthree}[1]{\reviewerresponse{green!20!white}{R3: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi
\ifnum\CommentsR=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\reviewerone{Restated theorem 2 and gave formal proof}
\linkinformal*
\begin{proof}
	By Theorem~\ref{thm:thickened-separated}, we know that if $L$ embeds $\ell$, then there exists an $\epsilon$ such that Construction~\ref{const:eps-thick-link} provides at least one $\epsilon$-separated link $\psi$ with respect to $L$ and $\ell$.
	Moreover, by Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
\end{proof}

@@

Applying Construction \ref{const:eps-thick-link} also enables one to verify the consistency of a given proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.

@@

\reviewertwo{Comment 3}
Observe that while the Weston-Watkins hinge loss was originally designed as a surrogate for $0-1$ loss in multiclass settings, there is no link such that $(L^{WW}, \psi)$ is consistent with respect to $\ell^{0-1}$. 
However, we can construct a polyhedral surrogate and use the canonical argmax link for $\ell^{0-1}$ by simply using the $L^k$ surrogate with $k=1$. 
The $L^k$ surrogate simplifies to 
\begin{align*}
	L^1(u)_y &= \left(\max_m \frac{m-1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
\jessie{Does this simplify further? I don't think so}

@@

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions and insights,
Stephen Becker for a reference to Hoffman constants,
and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.\raft{others?}
This material is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.

@@

>>>>

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\CommentsR}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\reviewerresponse}[2]{\ifnum\CommentsR=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}} % RF: I always read this as "propose dadd"
\newcommand{\reviewerone}[1]{\reviewerresponse{orange!20!white}{R1: #1}}
\newcommand{\reviewertwo}[1]{\reviewerresponse{blue!20!white}{R2: #1}}
\newcommand{\reviewerthree}[1]{\reviewerresponse{green!20!white}{R3: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi
\ifnum\CommentsR=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\reviewerone{Restated theorem 2 and gave formal proof}
\linkinformal*
\begin{proof}
	From Theorem~\ref{thm:thickened-separated}, since $L$ embeds $\ell$, there exists $\epsilon>0$ such that Construction~\ref{const:eps-thick-link} yields a link $\psi$ which is $\epsilon$-separated with respect to $L$ and $\ell$.
	By Theorem~\ref{thm:calibrated-separated}, since $\psi$ is $\epsilon$-separated for $L$ and $\ell$, the pair $(L,\psi)$ is calibrated with respect to $\ell$.
\end{proof}

@@

Applying Construction \ref{const:eps-thick-link} also enables one to verify the consistency of a given proposed link $\psi^*$.
For a given $\epsilon$ and norm $\|\cdot\|$, suppose one follows the routine of Construction~\ref{const:eps-thick-link} until the last step in which values for the link $\psi$ are selected.
Instead, we can simply test whether the proposed link values are contained in the valid choices, i.e., if $\psi^*(u) \in \Psi(u)$ for all $u\in\reals^d$.
If so, then the proposed link $\psi^*$ is calibrated.
See \S~\ref{sec:top-k} for an illustration of this test.
On the other hand, if $\psi^*$ cannot be produced from Construction \ref{const:eps-thick-link}, then it cannot be a calibrated link.
\reviewertwo{D}
This impossibility can be shown, for example, if there exists a point $u$ where $\Psi(u)$ is empty for all $\epsilon > 0$.

@@

\reviewertwo{Comment 3}
\raft{I made some wording edits here.  One general point though is to be careful when adding to the paper at this stage, since the notation was actually slightly off from what we had been doing, e.g.\ ``$0-1$ loss'' instead of ``0-1 loss''  and $\ell^{0-1}$ instead of $\ellzo$.}
Interestingly, by choosing $k=1$, one obtains what appears to be a novel surrogate for 0-1 loss in multiclass settings,
\begin{align*}
	L^1(u)_y &= \left(\max_{m\in\{1,\ldots,n\}} 1 - \frac{1}{m} + \frac 1 m \sum_{i=1}^m u_{[i]} \right) - u_y~.
\end{align*}
In particular, this surrogate is consistent with respect to 0-1 loss using the canonical argmax link, while the Weston-Watkins hinge is not consistent for any link (\S~\ref{sec:winge}).

@@

\mytodo{gray!20!white}{Cover: A}
Finally, a third proof of Theorem~\ref{thm:poly-ie-implies-consistent} is implicit in \citet[Theorem 8]{ramaswamy2016convex}.
The authors use an entirely different link construction involving the superprediction set of the surrogate loss.
We discuss their result and how it relates to our work in \S~\ref{app:ccdim-construction}.

@@

\subsection*{Acknowledgements}
We thank Arpit Agarwal and Peter Bartlett for many early discussions and insights,
Stephen Becker for a reference to Hoffman constants,
and Nishant Mehta, Enrique Nueve, and Anish Thilagar for other suggestions.
We thank Dhamma Kimpara for observations that led to \S~\ref{app:ccdim-construction}.
\raft{others?}
This material is based upon work supported by the National Science Foundation under Grant Nos.\ CCF-1657598, IIS-2045347, and DGE-1650115.

@@

\section{Connection to \citet[Theorem 8]{ramaswamy2016convex}}
\label{app:ccdim-construction}

\citet{ramaswamy2016convex} give an impressive array of consistency results for general prediction tasks.
Among them, in their Theorem 8, is a general sufficient condition for consistency.
We restate their result here in our notation.

\begin{theorem}[{\citet[Theorem 8]{ramaswamy2016convex}}]
  Let $\ell : \R \to \reals^\Y_+$ for $\R$ finite, and $L:\reals^d\to\reals^\Y_+$.
  Let $\gamma = \prop{\ell}$ and $\Gamma = \prop{L}$.
  Suppose there exists a finite set $\Sc \subset \reals^d$ such that $\bigcup_{u\in\Sc} \Gamma_u = \simplex$ and for each $u\in\Sc$ there exists $r\in\R$ such that $\Gamma_u\subseteq\gamma_r$.
  Then $L$ is calibrated with respect to $\ell$.
\end{theorem}

In other words, if there exists a finite representative set $\Sc \subset \reals^d$ for $L$ such that $L|_{\Sc}$ indirectly elicits $\gamma$, then $L$ is calibrated with respect to $\ell$.
Of course, if $L$ indirectly elicits $\gamma$ and has a finite representative set, then this condition holds.
Thus, not only does this result prove Theorem~\ref{thm:poly-ie-implies-consistent} for polyhedral surrogates, it also shows that the result extends to the setting of \S~\ref{sec:min-rep-sets}: surrogates with finite representative sets.

The crux of their result, as in ours, in the construction of a link function exhibiting calibration.
This construction is quite different from our Construction~\ref{const:eps-thick-link}, in that it operations in the loss vector space $\reals^\Y_+$ rather than the surrogate report space $\reals^d$.
Specifically, it operates on the \emph{superprediction set} $L(\reals^d) + \reals^\Y_+$, where the $+$ here is Minkowski addition.
An arbitrary element of the superprediction set is decomposed into a convex combination of elements of $L(\Sc)$, plus an element of $\reals^\Y_+$.
This convex combination is then thresholded at $1/|\Sc|$, where the link function may output $r\in\R$ if the weight on any $u\in\Sc$ with $\Gamma_u \subseteq \gamma_r$ is at least $1/|\Sc|$.
One can see that this construction does achieve separation, but does not necessarily align well with any norm in the surrogate report space.
It would be interesting to further compare the two constructions.
